### 2015-05-15 evaluation.tex
Done it.
URL and paper
address a comment

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\caption{Program statistics and race-checking results from applying \whoop and \corral on our benchmarks.}
\label{tab:stats}
\begin{tabular}{l rrr rr r}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\end{table}

\begin{table*}[t]
\small
\centering
\setlength{\tabcolsep}{0.45em}
\caption{Comparison with different yield instrumentation granularities and context-switch bounds.}
\label{tab:results}
\begin{tabular}{l r rrrr rrrr rrrr}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\end{table*}

\begin{figure}
\centering
\includegraphics[width=.99\linewidth]{experiments/figures/yieldmr_vs_yieldall.pdf}
\caption{Scatter plot showing the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. The symbols $+$, $\circ$ and $\times$, represent a context-switch bound of 2, 5 and 9, respectively.}
\label{fig:plot}
\end{figure}

@@

As an example of the second case, we found the following race in the generic\_nvram char driver (see Figure~\ref{fig:data_race_example}): in the \texttt{llseek} entry point the driver accesses the file offset \texttt{file->f\_pos} without a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This causes a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter.  We observed that another char driver, using the same APIs, \emph{does} use a mutex to protect the offset access in its \texttt{llseek} entry point, leading us to suspect that the race we found in generic\_nvram is not benign.  We have filed a bug report \ADComment{to whom?} and are awaiting a response.

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\caption{Program statistics and race-checking results from applying \whoop and \corral on our benchmarks.}
\label{tab:stats}
\begin{tabular}{l rrr rr r}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\vspace{-3mm}
\end{table}

\begin{table*}[t]
\small
\centering
\setlength{\tabcolsep}{0.45em}
\caption{Comparison with different yield instrumentation granularities and context-switch bounds.}
\label{tab:results}
\begin{tabular}{l r rrrr rrrr rrrr}
\centering
\input{experiments/tables/scalability.tex}
\end{tabular}
\vspace{-3mm}
\end{table*}

\begin{figure}
\centering
\includegraphics[width=.99\linewidth]{experiments/figures/yieldmr_vs_yieldall.pdf}
\vspace{-2mm}
\caption{Scatter plot showing the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. The symbols $+$, $\circ$ and $\times$, represent a context-switch bound of 2, 5 and 9, respectively.}
\label{fig:plot}
\vspace{-2mm}
\end{figure}

@@

As an example of the second case, we found the following race in the generic\_nvram driver (see Figure~\ref{fig:data_race_example}): in the \texttt{llseek} entry point the driver accesses the file offset \texttt{file->f\_pos} without a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This causes a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter.  We observed that another char driver, using the same APIs, \emph{does} use a mutex to protect the offset access in its \texttt{llseek} entry point, leading us to suspect that the race we found in generic\_nvram is not benign.  We have filed a bug report in the Linux kernel bug tracker and are awaiting a response.
